### 2024-11-10 conteudo/background/codeduplication.tex

Code Duplication Detection is a field in computer science studies that has the attention of researchers 
back to 1988 \citep{firstman}.
The occurrence of Code Duplication is a harmful artifact to have in software, affecting software-related 
tasks such as code readability, introduction of bugs, etc \citep{harmone}. 
In most cases, the occurrence of code duplication tends to create more unstable software 
than the nonduplicate code counterpart \citep{harmtwo} .

Through the years, the subject of studies related to Code Duplication Detection branched out mainly in 
two fields of study, Code Clone Detection and Code Plagiarism Detection, with the former focused on the 
technical aspect while the latter also introduced a social aspect of the field of research
\citep{litreview}. 
In this work, we are only interested in the Code Clone Detection branch given the nature of our work.

\subsection{Types of code clone duplication}

@@

The categorization of two artifacts as a duplication of each other can open the question of what is considered 
a duplication. To approach this question, the literature classified code duplication on the scale of the 
changes between the code artifacts, creating a classification of four types of code clone 
duplications \citep{litreview}. 
When comparing the two code artifacts, F and G, the four types of code duplication can be described 
as follows \citep{litreview}:

\begin{itemize}
	\begin{item}
		\textbf{Type-1:} The differences between F and G are in the context of revision of comments, variable names,
		white spaces, and any other kinds of irrelevant elements. Figure
		\ref{fig:type1} shows a typical example of Type-1 clone duplication 
		\citep{litreview}. 
	\end{item}
	\begin{item}
		\textbf{Type-2:} The differences between F and G are the same as type-1, with the addition of 
		considering the addition and deletion of redundant codes. Figure
		\ref{fig:type2} shows a typical example of Type-2 code clone duplication  \citep{litreview}. 
	\end{item}
	\begin{item}
		\textbf{Type-3:} The difference between F and G is the same as type-2, with the addition of considering 
		the reorder of code blocks, as well as statements within code blocks. Figure
		\ref{fig:type3} shows a typical example of 
		Type-3 code clone duplication \citep{litreview}. 
	\end{item}
	\begin{item}
		\textbf{Type-4:} The difference between F and G is the same as type-3, with the addition of considering 
		changes in data structures, the order of operands/operators in expressions, or replacing part of codes 
		with equivalent composition. Figure
		\ref{fig:type4} shows a typical example of Type-4 code clone duplication \citep{litreview}. 
	\end{item}

\end{itemize}

\begin{figure}
\includegraphics[scale=0.38]{types/type1}
\caption{Example of Type-1 code clone duplication.}
The example is based on the example presented by CHEN et al. \citep{litreview}. 
\label{fig:type1}
\end{figure}

\begin{figure}
\includegraphics[scale=0.38]{types/type2}
\caption{Example of Type-2 code clone duplication.}
The example is based on the example presented by CHEN et al. \citep{litreview}. 
\label{fig:type2}
\end{figure}

\begin{figure}
\includegraphics[scale=0.38]{types/type3}
\caption{Example of Type-3 code clone duplication.}
The example is based on the example presented by CHEN et al. \citep{litreview}. 
\label{fig:type3}
\end{figure}

\begin{figure}
\includegraphics[scale=0.38]{types/type4}
\caption{Example of Type-4 code clone duplication.}
The example is based on the example presented by CHEN et al. \citep{litreview}. 
\label{fig:type4}
\end{figure}

\subsection{Literature approches for code clone detection}

Given the passage of time, the literature developed many techniques and methods to approach the code clone 
detection problem. For a better understanding and analysis of these approaches, the literature divided the 
research done into five methodologies given the nature of their work  \citep{litreview}, which are:

\begin{itemize}
	\item \textbf{Textual-based approaches:}  The literature review made by Chen \citep{litreview}  
	states that this methodology is the first to be investigated by the literature. This methodology line 
	is based on seeing code as a text artifact and applying textual approaches for text similarity. One 
	example of this methodology applied is the work of Roy and Cordy
	\citep{textexample},
	which uses parsing and grammar techniques to detect code clones.

	\item \textbf{Token-based approaches:} This method tries to approach the problem by seeing the code in a
	similar way to the lexical analysis of the compiling process \citep{litreview}. 
	That means doing work along the lines of recognizing constants, keywords, and other specific programming 
	language tokens, mapping variables to representations to become naming-independent, etc. One example 
	of this methodology applied is the work of Toomey et al. \citep{tokenexample} 
	to detect code clones through hashed token sequences.

	\item \textbf{Tree-based approaches:} While the token-based approach uses the lexical analysis of the 
	compiling process, the tree-based approach uses the syntax tree. The syntax tree is a data structure that 
	stores the semantic information of a code artifact concerning the programming language \citep{compiler}. 
	One example of research that uses this information to detect code clones is done by Chilowicz and Duris
	\citep{treeexample}.

	\item \textbf{Metric-based approaches:} This methodology approaches the problem by extracting metrics 
	from the code artifact and using those metrics as an embedding representation of the artifact to measure 
	similarity \citep{litreview}, similar to the famous Word2Vec work done by Mikolov et al.
	\citep{wordtovec}. Examples of metrics can be program size, number of variables, number of access to
	memory, etc. One example of this methodology applied is the work done by Kaur and Sharm
	\citep{metricexample}.

	\item \textbf{Graph-based approaches:} Similarly to the Tree-based approaches, this methodology depends 
	heavily on an intermediate program representation, called program dependence graph (PDG) \citep{prodg}. 
	The representation stores information about the program’s control, statement, and data dependencies. 
	One example of this methodology applied is the recent work done by Liu et al. \citep{tailor},
	one of the state-of-the-art works in the field.

\end{itemize}

The state-of-the-art methods for code clone detection usually have high computational time and memory space 
usage, as well being programming language-specific approaches, which cannot be easily implemented in programming 
languages that were not used in their research \citep{litreview}. 
These are concerns for our research, and for this reason, we will use a generalist textual-based approach 
based solely on Natural Language Processing (NLP) text similarity detection methods, which we will introduce 
in Chapter \ref{cha:tool} and evaluate this approach in this work.

\subsection{Evaluating code duplication methods}

@@

Given the necessity to evaluate and compare approaches for code clone detection, it was developed and widely 
adopted: OJ-Clone, a dataset collected from a pedagogical online judge system \citep{ojclone},
and BigCloneBench, a dataset collected from over 25,000 Java software systems \citep{bigclonebench}. 
The existence of only two spread datasets is an open concern in literature as the limited scope of OJ-Clone 
and the problems of BigCloneBench presented by Krinke and Ragkhitwetsagul \citep{bigfail}. The BigCloneBench
is the dataset used by most of the literature works, given the limited pedagogical scope of the OJ-Clone.

To evaluate the code clone detection approaches against the datasets, the works compute metrics using 
the predictions made related to the instances of the dataset. There are four possible outcomes when an 
instance is predicted by a code clone detection approach, which are:

\begin{itemize}
	\begin{item}
		\textit{True positivity (TP)}: This outcome happens when the approach predicts that the instance 
		is a code clone and the instance is a code clone.
	\end{item}
	\begin{item}
		\textit{False positivity (FP)}: This outcome happens when the approach predicts that the instance 
		is a code clone, but the instance is not a code clone.
	\end{item}
		\begin{item}
		\textit{True negative (TN)}: This outcome happens when the approach predicts that the instance 
		is not a code clone and the instance is not a code clone.
	\end{item}
	\begin{item}
		\textit{False negative (FN)}: This outcome happens when the approach predicts that the instance 
		is not a code clone, but the instance is a code clone.
	\end{item}
\end{itemize}

Given the number of TP, FP, TN, and FN that resulted after an approach evaluation against a dataset,
it is possible to compute classical metrics such as Precision, Recall, and F-Score \citep{recall}.
In this work, we use the Recall metric as the code clone detection approaches usually make available 
this metric to compare themselves in contrast with the others. The Recall metric is defined by the 
following formula \citep{recall}:

@@

Where $\sum TP$ is the number of true positives in the evaluation and $\sum FN$ is the number of 
false negatives. The Recall metric is a number between $0$ and $1$, where a value closer to $1$ is 
better, and a value closer to $0$ is worse.

>>>>

Code Duplication Detection is a field in computer science that has attracted
researchers' attention since 1988 \citep{firstman}. The presence of code
duplication is considered a harmful artifact in software, as it negatively
affects tasks such as code readability and increases the likelihood of
introducing bugs \citep{harmone}. In most cases, code duplication tends to make
software more unstable compared to its non-duplicated counterpart
\citep{harmtwo}.

Over the years, research on Code Duplication Detection has branched into two
main areas: Code Clone Detection and Code Plagiarism Detection. The former
focuses on technical aspects, while the latter incorporates social dimensions
into the research field \citep{litreview}. In this work, we focus solely on the
Code Clone Detection branch due to the nature of our study.

\subsection{Types of Code Clone Duplication}

@@

The classification of two code artifacts as duplicates raises the question of
what constitutes duplication. To address this, the literature categorizes code
duplication based on the extent of differences between code artifacts,
resulting in four types of code clone duplications \citep{litreview}. When
comparing two code artifacts, F and G, the four types of code duplication can
be described as follows \citep{litreview}:

\begin{itemize}
    \begin{item}
	\textbf{Type-1 (T1):} The differences between F and G are limited to
	    changes in comments, variable names, white spaces, and other
	    irrelevant elements. Figure \ref{fig:type1} shows a typical example
	    of Type-1 clone duplication \citep{litreview}.
    \end{item}
    \begin{item}
	\textbf{Type-2 (T2):} The differences between F and G include those
	    from Type-1, along with the addition and deletion of redundant
	    code. Figure \ref{fig:type2} shows a typical example of Type-2 code
	    clone duplication \citep{litreview}.
    \end{item}
    \begin{item}
	\textbf{Type-3 (T3):} The differences between F and G include those
	    from Type-2, as well as reordering code blocks and statements
	    within code blocks. Figure \ref{fig:type3} shows a typical example
	    of Type-3 code clone duplication \citep{litreview}.
    \end{item}
    \begin{item}
	\textbf{Type-4 (T4):} The differences between F and G include those
	    from Type-3, along with changes in data structures, the order of
	    operands/operators in expressions, or the replacement of code parts
	    with equivalent compositions. Figure \ref{fig:type4} shows a
	    typical example of Type-4 code clone duplication \citep{litreview}.
    \end{item}
\end{itemize}

\begin{figure}
\includegraphics[scale=0.38]{types/type1}
\caption{Example of Type-1 code clone duplication.}
The example is based on the work presented by CHEN et al. \citep{litreview}.
\label{fig:type1}
\end{figure}

\begin{figure}
\includegraphics[scale=0.38]{types/type2}
\caption{Example of Type-2 code clone duplication.}
The example is based on the work presented by CHEN et al. \citep{litreview}.
\label{fig:type2}
\end{figure}

\begin{figure}
\includegraphics[scale=0.38]{types/type3}
\caption{Example of Type-3 code clone duplication.}
The example is based on the work presented by CHEN et al. \citep{litreview}.
\label{fig:type3}
\end{figure}

\begin{figure}
\includegraphics[scale=0.38]{types/type4}
\caption{Example of Type-4 code clone duplication.}
The example is based on the work presented by CHEN et al. \citep{litreview}.
\label{fig:type4}
\end{figure}

\subsection{Literature Approaches for Code Clone Detection}

Over time, various techniques and methods have been developed in the literature
to address the code clone detection problem. For better analysis and
understanding, these approaches are categorized into five methodologies based
on their characteristics \citep{litreview}:

\begin{itemize}
    \item \textbf{Textual-based approaches:} According to Chen’s literature 
    review \citep{litreview}, this is the earliest methodology explored in 
    the field. It treats code as a text artifact and applies textual similarity
    techniques. An example is the work of Roy and Cordy \citep{textexample}, 
    which uses parsing and grammar techniques to detect code clones.

    \item \textbf{Token-based approaches:} This method tackles the problem 
    similarly to lexical analysis in the compilation process \citep{litreview}. 
    It involves identifying programming language tokens such as constants and 
    keywords, mapping variables to independent representations, etc. An example
    is the work of Toomey et al. \citep{tokenexample}, which detects code 
    clones through hashed token sequences.

    \item \textbf{Tree-based approaches:} While token-based approaches utilize
     lexical analysis, tree-based approaches rely on syntax trees, which store
     semantic information of code artifacts based on the programming language
     \citep{compiler}. An example of this approach is the work by Chilowicz 
     and Duris \citep{treeexample}.

    \item \textbf{Metric-based approaches:} This methodology uses extracted 
    metrics from code artifacts as embedding representations to measure 
    similarity \citep{litreview}, akin to the Word2Vec model by Mikolov et al. 
    \citep{wordtovec}. Metrics can include program size, number of variables, 
    memory access counts, etc. An example is the work by Kaur and Sharma \citep{metricexample}.

    \item \textbf{Graph-based approaches:} Similar to tree-based approaches, 
    this methodology depends on intermediate program representations, 
    specifically the program dependence graph (PDG), which stores information 
    on control, statements, and data dependencies \citep{prodg}. A recent 
    example is the work by Liu et al. \citep{tailor}, which represents one of 
    the state-of-the-art works in the field.
\end{itemize}

State-of-the-art code clone detection methods typically require substantial
computational time and memory, and many are language-specific, limiting their
applicability across different programming languages \citep{litreview}. Given
these constraints, we opted for a generalist textual-based approach using
Natural Language Processing (NLP) text similarity methods, which we will
introduce in Chapter \ref{cha:tool} and evaluate in this work.

\subsection{Evaluating Code Duplication Methods}

@@

To evaluate and compare code clone detection methods, two widely adopted
datasets are available: OJ-Clone, collected from a pedagogical online judge
system \citep{ojclone}, and BigCloneBench, compiled from over 25,000 Java
software systems \citep{bigclonebench}. However, literature has expressed
concerns over the limited scope of OJ-Clone and the issues with BigCloneBench
identified by Krinke and Ragkhitwetsagul \citep{bigfail}. Despite these
limitations, BigCloneBench is commonly used due to the limited pedagogical
scope of OJ-Clone.

BigCloneBench further divides Type-3 duplications into three categories—Weak
Type-3 (WT3), Medium Type-3 (MT3), and Strong Type-3 (ST3)—where WT3 is closer
to Type-4 and ST3 is closer to Type-2 \citep{bigclonebench}. This results in
six possible outcomes for a code pair: Type-1, Type-2, Strong Type-3, Medium
Type-3, Weak Type-3/Type-4, and non-duplicate \citep{bigclonebench}.

To assess code clone detection methods against these datasets, researchers
calculate metrics based on the model’s predictions. There are four possible
outcomes for each prediction:

\begin{itemize}
    \begin{item}
        \textit{True Positivity (TP):} The model correctly identifies an instance as a code clone.
    \end{item}
    \begin{item}
        \textit{False Positivity (FP):} The model incorrectly identifies a non-clone instance as a code clone.
    \end{item}
    \begin{item}
        \textit{True Negative (TN):} The model correctly identifies an instance as non-clone.
    \end{item}
    \begin{item}
        \textit{False Negative (FN):} The model incorrectly identifies a clone instance as non-clone.
    \end{item}
\end{itemize}

Using the counts of TP, FP, TN, and FN, standard metrics such as Precision,
Recall, and F-Score can be calculated \citep{recall}. In this work, we focus on
the Recall metric, as it is commonly reported in literature for comparing code
clone detection approaches. Recall is defined as follows \citep{recall}:

@@

Where $\sum TP$ is the total number of true positives, and $\sum FN$ is the
total number of false negatives. Recall values range between 0 and 1, with
values closer to 1 indicating better performance.

### 2024-11-10 conteudo/introduction/intro.tex

\section**{Problem outline}
\label{sec:problem}

@@

This research aims to identify patterns of software engineering techniques,
such as refactoring methods commonly used to address code duplications. These
patterns will serve as a guide for future contributors in mitigating code
duplication issues within this context. To investigate our approach, we use the
initial version of our tool to identify duplicate code in the Linux kernel,
specifically targeting parts of the AMD Display driver code. We will then
refactor portions of this code and submit patches to maintainers, providing
evidence of the tool's accuracy in detecting duplicate functions.

Our research design follows a multi-method approach, utilizing various
methodologies to answer our research questions. We have structured the study
into two phases, each employing different research methods.

@@

This manuscript consists of five more chapters. Chapter \ref{cha:back} presents
the literature overview for code duplication detection (main definitions,
current approaches in the literature), a brief description of the Linux kernel,
and a review of refactoring methods used throughout this research. Chapter
\ref{cha:tool} presents our proposed tool to detect code duplication in the
Linux kernel, describing all the main components.  Chapter \ref{cha:method}
describes the research methods selected to guide our work. Chapter
\ref{cha:eval} shows the results obtained from the research methods to evaluate
our proposed tool. Chapter \ref{cha:results} presents the current research
stage and the work plan, with the addition of preliminary results obtained.

>>>>

@@

This research aims to identify patterns of software engineering techniques, such as refactoring methods commonly used to address code duplications. These patterns will serve as a guide for future contributors in mitigating code duplication issues within this context. To investigate our approach, we are developing a tool to identify duplicate code in the Linux kernel, explicitly targeting parts of the AMD Display driver code. We are then refactoring portions of this code and submitting patches to maintainers, providing evidence of the tool's accuracy in detecting duplicate functions. Our research design follows a multi-method approach, structured into two phases, each employing different research methods.

@@

This manuscript consists of five more chapters. Chapter \ref{cha:back} presents
the literature overview for code duplication detection (main definitions,
current approaches in the literature), a brief description of the Linux kernel,
and a review of refactoring methods used throughout this research. Chapter
\ref{cha:tool} presents our proposed tool to detect code duplication in the
Linux kernel, describing all the main components.  Chapter \ref{cha:method}
describes the research methods selected to guide our work. Chapter
\ref{cha:results} shows the first results obtained from the research methods to evaluate
our proposed tool and presents the current research stage and the work plan,
with the addition of a discussion about our preliminary results.

### 2024-11-10 conteudo/preliminar/results.tex

Base Content of the Preliminar Results of the research. TODO.

>>>>

\section{Final Remarks}

We have completed Phase 1 of our research, during which we developed our proposed tool and evaluated it using the BigCloneBench dataset and through empirical analyses. The results indicate our tool can identify code clone duplications within the Linux kernel.

As the next step, we plan to conduct an ethnographic study as outlined in Section \ref{sec:meteth}. To preliminarily assess the potential impact of this research, we applied our systematic approach for mitigating code duplication to two pairs of functions. Table \ref{tab:patch} presents the initial results obtained from this process.

\input{conteudo/preliminar/table_patch}

In the first function pair, completing the refactoring requires the expertise of a maintainer for the AMD Display driver. This observation is because duplicated code artifacts involve copy-pasted code that imports different configuration files. The design of the AMD Display driver configuration files necessitates importing specific configurations at compile time, which prevents a generic approach. Consequently, refactoring this pair requires changes in how the AMD Display driver manages configuration files -- a complex task that demands input from an expert or maintainer.

The refactoring of the second function pair, however, was successful. We submitted this refactoring as a patch to the AMD Display driver to obtain feedback from the maintainers.
\todo[inline]{Atualizar ... tentar colocar algo do feedback que recebeu da revisão do patch}

\input{conteudo/preliminar/cronograma}
\todo[inline]{Atualizar o cronograma, alocando tempo para evolucao da ferramenta}

Finally, as indicated in our proposed schedule in Table \ref{fig:cronograma}, our upcoming tasks include conducting the complete ethnographic study. This step will start with completing our systematic approach to code duplication mitigation. Once we have finalized the mitigations, we intend to submit them to the AMD Display driver mailing list to gather insights and feedback from the maintainers regarding the changes we implemented.

\todo[inline]{colocar aqui também algo da evolucao da ferramenta que sera feito até o final do mestrado}

### 2024-11-10 conteudo/tool/functionalities.tex
remove comment about trie, would be a waste and too deep

\section{Tool functionalities}
\label{subsec:func}

We propose three main functionalities for the user in the tool, called duplication explorer,
function information, and duplication relatory. Each of the functionalities receives its 
adequated parameters to execute, except an optional parameter shared by all of them, which 
is minimum similarity per query. The minimum similarity per query is not the same as the 
minimum similarity presented in \ref{subsec:setup}, as it enables a volatile change in the minimum 
similarity interest in a query-specific context. There is an explanation of each of the 
main functionalities in this section.

\subsection{Duplication explorer}

The duplication explorer is the principal functionality of our tool. The functionality's
purpose is to expose the user to the duplicated function pairs found by our tool. We 
implement optional filter methods to enable more complex queries, as described below. 
Figure \ref{fig:explorer_ex} demonstrates the functionality usage.

\begin{itemize}
	\begin{item}
		\textbf{Sorting filter:} This filter enables the user to sort the results by the 
		similarity of the function pairs or by the number of duplicated lines. By default, 
		the tool sorts by similarity, and the user can pass a sort parameter to change 
		the sorting method.
	\end{item}

	\begin{item}
		\textbf{Limiter filter:} This filter receives a number parameter named limiter 
		by the user, which limits the number of results shown to the user by this given number.
	\end{item}

	\begin{item}
		\textbf{Pattern filter:} This filter makes the explorer ignore every pair 
		of duplicated functions that do not match a pattern given by the user as a parameter.
		We say that a function matches a pattern if the string formed by the concatenation 
		of the relative path of the code file plus the function name contains the pattern 
		as a substring. The user can define if both functions or at least one of the 
		functions in the pair need to match the pattern by giving a specific parameter.
	\end{item}
\end{itemize}

\begin{figure}
\includegraphics[scale=0.5]{explorer_example}
\caption{Explorer Example}
\label{fig:explorer_ex}
\end{figure}

\subsection{Function information}

\label{subsec:functioncommand}

The Function information purpose is to give more in-depth information about a specific 
function. The functionality receives a function the user is interested in and then 
informs the user about the relative path, the function name, and the lines the function 
is defined for the function the user is interested in and for every function that is a 
duplication of the given function. There can be multiple functions with the same name 
in a codebase. To distinguish them, we receive a pattern string from the user, and we 
use the first function to find one that matches the given pattern. We say that a 
function matches a pattern if the string formed by the concatenation of the relative 
path of the code file plus the function name contains the pattern as a substring. 
Figure \ref{fig:function_ex} demonstrates the functionality usage.

\begin{figure}
\includegraphics[scale=0.5]{function_example}
\caption{Function Example}
\label{fig:function_ex}
\end{figure}

\subsection{Duplication relatory}

The duplication relatory purpose is to give an overview of the input codebase. 
The functionality extracts how many lines of duplicated code per folder in the 
codebase and presents it to the user in a reasonable format. To extract the 
information, we use the Code Duplication Database to list the duplicated functions 
and the temporary code to know how many lines the duplication functions have. 
Figure \ref{fig:relatory_ex} demonstrates the functionality usage. 
(DO I TALK ABOUT THE TRIE USAGE TO MAINTAIN THE HIERARCHICAL TREE STRUCTURE? I THINK NOT)

\begin{figure}
\includegraphics[scale=0.5]{relatory_example}
\caption{Function Example}
\label{fig:relatory_ex}
\end{figure}

>>>>

\section{Tool Functionalities}
\label{subsec:func}

We propose three main functionalities for the user in the tool, called the \textbf{Duplication Explorer}, \textbf{Function Information}, and \textbf{Duplication Report}. Each functionality accepts specific parameters to perform its operations, with an optional parameter shared by all: \textbf{minimum similarity per query}. This minimum similarity per query is distinct from the minimum similarity setting introduced in Section \ref{subsec:setup}, as it enables a dynamic adjustment of the similarity threshold within a query-specific context. Below is an explanation of each of these main functionalities.

\subsection{Duplication Explorer}

The Duplication Explorer is the primary functionality of our tool, designed to present the user with pairs of duplicated functions identified by the tool. We implement optional filters to facilitate more complex queries, as described below. Figure \ref{fig:explorer_ex} demonstrates an example of this functionality in use.

\begin{figure}
\includegraphics[scale=0.5]{explorer_example}
\caption{Example of the \textit{Duplication Explorer} functionality of the proposed tool in action.}
\label{fig:explorer_ex}
\end{figure}

\begin{itemize}
	\item \textbf{Sorting Filter:} This filter allows the user to sort the results by the similarity score of the function pairs or by the number of duplicated lines. By default, the tool sorts results by similarity, but the user can pass a sorting parameter to switch the sorting method.

	\item \textbf{Limiter Filter:} This filter accepts a numerical parameter, called a limiter, which restricts the number of results displayed to the user to the specified number.

	\item \textbf{Pattern Filter:} This filter allows the Duplication Explorer to ignore duplicated function pairs that do not match a user-defined pattern. A function matches a pattern if the string is formed by concatenating the relative path of the code file with the function name, which contains the pattern as a substring. The user can specify whether both functions in the pair must match the pattern or if matching one of the functions is sufficient.
\end{itemize}

\subsection{Function Information}
\label{subsec:functioncommand}

The purpose of the Function Information functionality is to provide detailed information about a specific function. The functionality receives a target function from the user and returns information such as the relative path, function name, and line numbers where the function is defined. Additionally, it provides similar information for every function that duplicates the given function.

\begin{figure}
\includegraphics[scale=0.5]{function_example}
\caption{Example of the \textit{Function Information} functionality of the proposed tool in action.}
\label{fig:function_ex}
\end{figure}

Since multiple functions with the same name may exist in a codebase, the user can provide a pattern string to differentiate them. A function matches a pattern if the concatenated string of the relative path and function name contains the pattern as a substring. Figure \ref{fig:function_ex} demonstrates this functionality in action.

\subsection{Duplication Report}

The purpose of the Duplication Report functionality is to provide an overview of duplicated code within the input codebase. This functionality calculates the number of duplicated lines per folder in the codebase and presents the information to the user in a readable format.

\begin{figure}
\includegraphics[scale=0.5]{relatory_example}
\caption{Example of the \textit{Duplication Report} functionality of the proposed tool in action.}
\label{fig:relatory_ex}
\end{figure}

The tool utilizes the Code Duplication Database to list duplicated functions and the temporary codebase to determine the line count for these functions to generate this report. Figure \ref{fig:relatory_ex} demonstrates an example of this functionality in action.

### 2024-11-10 conteudo/tool/tool.tex

The tool operates in two main steps. The first step, called *Setup*, is
executed only once for each codebase. This step processes the codebase by
extracting functions from code files and identifying code clone duplications.
The second step, called *Query Responder*, utilizes the information obtained in
the Setup phase to execute the tool’s functionalities as needed. Detailed
descriptions of the Setup and Query Responder processes can be found in
Sections \ref{subsec:architecture} and \ref{subsec:func}.

>>>>

The tool operates in two main steps. The first step, called \textbf{Setup}, is
executed only once for each codebase. This step processes the codebase by
extracting functions from code files and identifying code clone duplications.
The second step, called \textbf{Query Responder}, utilizes the information obtained in
the Setup phase to execute the tool functionalities as needed. Detailed
descriptions of the Setup and Query Responder processes can be found in
Sections \ref{subsec:architecture} and \ref{subsec:func}.
